---
title: "ETF3231/5231 Business Forecasting"
page-layout: full
---

```{r}
#| label: load_packages
#| include: false
#| message: false
#| warning: false
#| echo: false
#| cache: false
library(tidyverse)
options(knitr.kable.NA = '')
source(here::here("course_info.R"))
```

Business Forecasting focuses on practical forecasting workflows with R, from first visual diagnostics through ETS, ARIMA, and regression-based models. The site is organised the same way as the week-to-week teaching: use the current-week panel to get oriented, then drop into the relevant week page for readings, seminar slides, activities, and assessment reminders.

## This week

```{r}
#| output: asis
#| cache: false
show_week_dashboard()
```

::: {.action-grid}
<a class="action-card" href="https://learning.monash.edu/course/view.php?id=26702">
  <span class="action-card__kicker">Start here</span>
  <strong>Moodle</strong>
  <span>Announcements, assessment instructions, unit administration, and official submission links.</span>
</a>
<a class="action-card" href="https://echo360.net.au/section/630d3bbb-85b4-47c8-842d-4bafc932413d/home">
  <span class="action-card__kicker">Watch</span>
  <strong>Recordings</strong>
  <span>Lecture recordings and supporting video material for each teaching week.</span>
</a>
<a class="action-card" href="https://edstem.org/au/courses/30990">
  <span class="action-card__kicker">Ask questions</span>
  <strong>Discussion</strong>
  <span>Use Ed for clarifications, course questions, and help between classes.</span>
</a>
<a class="action-card" href="#weekly-schedule">
  <span class="action-card__kicker">Plan ahead</span>
  <strong>Weekly schedule</strong>
  <span>See the sequence of topics, textbook chapters, quizzes, and assignment deadlines.</span>
</a>
:::

## Unit at a glance

::: {.metric-grid}
<div class="metric-card">
  <span class="metric-card__label">Seminar and workshop</span>
  <strong>Wednesday 3:00pm to 4:50pm</strong>
  <span>Building K Level 3, K321, Caulfield campus.</span>
</div>
<div class="metric-card">
  <span class="metric-card__label">Tutorials</span>
  <strong>Thursday to Friday</strong>
  <span>Weekly 50-minute tutorial classes across multiple streams.</span>
</div>
<div class="metric-card">
  <span class="metric-card__label">Core method set</span>
  <strong>ETS, ARIMA, regression</strong>
  <span>Move from graphical diagnostics through benchmark, state space, and regression-based forecasting.</span>
</div>
<div class="metric-card">
  <span class="metric-card__label">Assessment</span>
  <strong>Quizzes, IAs, GAs, final exam</strong>
  <span>In-semester work contributes 40%; the final exam contributes 60%.</span>
</div>
:::

## Learning outcomes

::: {.outcome-grid}
<div class="outcome-card">
  <span class="outcome-card__number">01</span>
  <p>Diagnose the main features of time series data using graphics, decomposition, and residual analysis.</p>
</div>
<div class="outcome-card">
  <span class="outcome-card__number">02</span>
  <p>Build and compare forecasting models ranging from benchmark methods to ETS and ARIMA families.</p>
</div>
<div class="outcome-card">
  <span class="outcome-card__number">03</span>
  <p>Use predictors, regression structure, and dynamic regression to improve forecasts when extra information is available.</p>
</div>
<div class="outcome-card">
  <span class="outcome-card__number">04</span>
  <p>Communicate forecasts clearly in Quarto-based analytical reports and reproducible R workflows.</p>
</div>
:::

## Teaching team and support

::: {.split-grid}
<div class="resource-card">
  <span class="resource-card__kicker">Teaching team</span>
  <h3>Who is teaching this unit</h3>
  <ul>
    <li><a href="https://research.monash.edu/en/persons/george-athanasopoulos"><strong>George Athanasopoulos</strong></a>. Lecturer and Chief Examiner. Email: <a href="mailto:George.Athanasopoulos@monash.edu">George.Athanasopoulos@monash.edu</a></li>
    <li><strong>Ari Handayani</strong>, tutor</li>
    <li><strong>Joan Tan</strong>, tutor</li>
    <li><strong>Sombut Jaidee</strong>, tutor</li>
    <li><strong>Weiben Zhang</strong>, tutor</li>
  </ul>
</div>
<div class="resource-card">
  <span class="resource-card__kicker">Consultations</span>
  <h3>Weekly support options</h3>
  <ul>
    <li>Monday 12 to 1pm. Joan Tan. Room H4.68 and <a href="https://monash.zoom.us/j/89771462448?pwd=t0M6BDuWVit1qypb9aKvw68zkBfWTq.1">Zoom</a>.</li>
    <li>Tuesday 11 to 12:30pm. Ari Handayani. Room H4.63 and <a href="https://monash.zoom.us/j/89771462448?pwd=t0M6BDuWVit1qypb9aKvw68zkBfWTq.1">Zoom</a>.</li>
    <li>Tuesday 4 to 5pm. Weiben Zhang. <a href="https://monash.zoom.us/j/89771462448?pwd=t0M6BDuWVit1qypb9aKvw68zkBfWTq.1">Zoom</a>.</li>
    <li>Thursday 11 to 11:30am. Ari Handayani. <a href="https://monash.zoom.us/j/89771462448?pwd=t0M6BDuWVit1qypb9aKvw68zkBfWTq.1">Zoom</a>.</li>
    <li>Thursday 2 to 3pm. George Athanasopoulos. <a href="https://monash.zoom.us/j/88353896610?pwd=cQfs6cajR3kQCFakBoFrjZLrSArstq.1">Zoom</a>.</li>
    <li>Friday 1 to 2pm. Ari Handayani. <a href="https://monash.zoom.us/j/89771462448?pwd=t0M6BDuWVit1qypb9aKvw68zkBfWTq.1">Zoom</a>.</li>
    <li>Friday 5 to 6pm. Sombut Jaidee. Room H4.69 and <a href="https://monash.zoom.us/j/89771462448?pwd=t0M6BDuWVit1qypb9aKvw68zkBfWTq.1">Zoom</a>.</li>
  </ul>
</div>
<div class="resource-card">
  <span class="resource-card__kicker">Core reference</span>
  <h3>Textbook and software setup</h3>
  <ul>
    <li><a href="https://otexts.com/fpp3/"><em>Forecasting: Principles and Practice</em></a> is the main text for the unit.</li>
    <li>Install the core packages with <code>install.packages(c("tidyverse","fpp3","GGally"), dependencies = TRUE)</code>.</li>
    <li>Use the weekly pages for the exact reading sections and preparation tasks.</li>
  </ul>
</div>
:::

## Weekly schedule

Each week combines textbook reading, video preparation, the Wednesday seminar and workshop block, and tutorial support. Use the week pages for readings, slides, activities, and upcoming deadlines.

```{r}
#| label: schedule2
#| message: false
#| warning: false
#| echo: false
#| output: asis
current_week <- get_current_week_context()$current$Week[[1]]

schedule |>
  mutate(
    week_num = Week,
    Week = case_when(
      is.na(week_num) ~ "<span class='week-pill week-pill--break'>Break</span>",
      week_num == current_week ~ glue::glue("<span class='week-pill week-pill--current'>Week {week_num}</span>"),
      TRUE ~ glue::glue("<span class='week-pill'>Week {week_num}</span>")
    ),
    Date = format(Date + 2, "%d %b"),
    Topic = case_when(
      is.na(week_num) ~ "<span class='muted'>Mid-semester break</span>",
      TRUE ~ glue::glue("<a href='./week{week_num}/index.html'>{Topic}</a>")
    ),
    Reading = case_when(
      is.na(Chapter) ~ "<span class='muted'>&mdash;</span>",
      TRUE ~ glue::glue("<a href='{Chapter_URL}'>{Chapter}</a>")
    ),
    Deadlines = pmap_chr(
      list(Assignment, File, Quiz),
      \(assignment, file, quiz) {
        links <- character()
        if (!is.na(assignment)) {
          html_file <- paste0(tools::file_path_sans_ext(file), ".html")
          links <- c(links, glue::glue("<a class='mini-link' href='{html_file}'>{assignment}</a>"))
        }
        if (!is.na(quiz)) {
          links <- c(links, glue::glue("<span class='mini-link'>{quiz}</span>"))
        }
        if (length(links) == 0) "<span class='muted'>&mdash;</span>" else paste(links, collapse = " ")
      }
    )
  ) |>
  select(Week, Date, Topic, Reading, Deadlines) |>
  knitr::kable(
    format = "html",
    escape = FALSE,
    table.attr = "class='table course-table'"
  )
```

## Assessments

::: {.assessment-grid}
<a class="assessment-card" href="assignments/A1.html">
  <span class="assessment-card__kicker">Individual work</span>
  <strong>IA1 to IA4</strong>
  <span>Four individual assignments across the semester, increasing in weight from 2% to 15%.</span>
</a>
<a class="assessment-card" href="assignments/G1.html">
  <span class="assessment-card__kicker">Group work</span>
  <strong>GA1 to GA4</strong>
  <span>ETF5231 group assignments running alongside the individual tasks.</span>
</a>
<a class="assessment-card" href="https://learning.monash.edu/course/view.php?id=26702">
  <span class="assessment-card__kicker">Weekly rhythm</span>
  <strong>Workshop quizzes</strong>
  <span>Weekly quizzes completed during workshops, with the best eight contributing the core 8%.</span>
</a>
<a class="assessment-card" href="https://learning.monash.edu/course/view.php?id=26702">
  <span class="assessment-card__kicker">Final hurdle</span>
  <strong>Final exam</strong>
  <span>The exam contributes 60% of the total mark, with in-semester work contributing the remaining 40%.</span>
</a>
:::

ETF5231 students combine individual and group assignment results with weights 0.7 and 0.3 respectively. The due dates can move slightly as the semester unfolds, so Moodle remains the final source of truth for submission timing.

Presentation requirements remain Quarto-based unless otherwise specified, and AI use must be declared according to the assessment instructions. Standard Monash late penalties apply; see the [Marking and Feedback Procedure](https://publicpolicydms.monash.edu/Monash/documents/1935752) for the formal policy.

::: {.callout-tip title="Group Participation - ETF5231 Students ONLY"}

Group participation rules for group assignments (GAs): It is expected that all group members participate equally to the group assignments. It sometimes helps to keep a log of the tasks each member is to complete. This may assist in keeping some balance throughout the semester. To ensure that all group members are contributing the following rules will apply for all the group assignments throughout the semester.

Every group member has the right to express concern/dislike in terms of a group member being absent from group activities. This has to be expressed directly to me (and only me) via a formal email stating facts that have hindered the operations of the group (saying I do not like George because he is tall is not a reason for expressing concern). If at least two such complaints are submitted during the completion of an assignment, the group member concerned will receive a warning. If the situation is not improved during the next assignment and another two complaints are again submitted, the group member will be immediately removed from the group and will be expected to complete the rest of the group assignments alone. 
:::

## Install the R packages

Use the following once if you need the core packages for the semester.

```r
install.packages(c("tidyverse","fpp3", "GGally"), dependencies = TRUE)
```
