---
title: "Week 12: Review"
---

```{r}
week <- 12
source(here::here("course_info.R"))
```

## Tutorial exercises

-   Complete Exercises 1-7 from [Section 10.7 of the book](https://otexts.com/fpp3/dynamic-exercises.html).
-   [Tutorial learning objectives](tute-lo.qmd).
-   <i class="bi bi-download"></i> [Week 12 Tutorial Solution.html](Tutorial12Solution.html){download="Week 12 Tutorial Solution.html"}


## What you will learn this week

* Review Assignment 1
* Announce winner of the forecasting competition
* Discuss exam

## Pre-seminar activities

Catch up on any exercises not yet done

```{r}
#| output: asis
show_slides(week)
```


## Post-class activities

* Do any exercises not yet finished.
* Complete past exams: [[2022](Exam2022.pdf)] [[2023](Exam2023.pdf)] [[2024](Exam2024.pdf)]

<!-- * Exam solutions: [[2023](/exams/Exam2023_solutions.pdf)] [[2024](/exams/Exam2024_solutions.pdf)] -->

* Exam solutions: [[2022](Exam2022_solutions.pdf)]


* Re-read the textbook
* Listen again to all lectures


