---
title: "Week 6: Exponential smoothing"
---

```{r}
week <- 6
source(here::here("course_info.R"))
```

## Tutorial exercises

-   Complete Exercises 1-5 from [Section 8.8](https://otexts.com/fpp3/expsmooth-exercises.html).
-   [Tutorial learning objectives](tute-lo.qmd).
<!-- -   <i class="bi bi-download"></i> [Week 6 Tutorial Solution.html](Week6.html){download="Week 6 Tutorial Solution.html"} -->


## What you will learn this week

* Exponential smoothing methods with trend and seasonality
* ETS models
* Automatic model selection using the AICc


## Pre-seminar activities

Read [Sections 8.4-8.7 of the textbook](https://otexts.com/fpp3/expsmooth.html) and watch all embedded videos.

<!-- ```{r} -->
<!-- #| output: asis -->
<!-- show_slides(week) -->
<!-- ``` -->

## Seminar activities

```{r}
#| child: activities.md
```


## Seminar code

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [week6.R](week6.R){download="week6.R"}
:::



```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
