---
title: "Week 1: What is forecasting?"
---

```{r}
week <- 1
source(here::here("course_info.R"))
```

## What you will learn this week

* How to think about forecasting from a statistical perspective
* What makes something easy or hard to forecast?
* Using the `tsibble` package in R

## Pre-class activities

Before we start classes, make sure you are familiar with R, RStudio and the tidyverse packages. If you've already done one of ETX2250/ETC1010 or something equivalent you should be fairly familiar with these concepts and probably will not need much help. If you're new to R and the tidyverse, then you will need to get yourself up-to-speed. 

-   Install/update R, RStudio. See [https://otexts.com/fpp3/appendix-using-r.html](https://otexts.com/fpp3/appendix-using-r.html)
-   Install required packages `install.packages(c("tidyverse","fpp3", "GGally"), dependencies = TRUE)`
-   Explore StartR: [https://startr.numbat.space/](https://startr.numbat.space/). Work through **Getting started** (5 modules) and **Writing documents** (1 module). Do as much of it as you think you need. For those students new to R, it is strongly recommended that you do all these. For those who have previously used R, concentrate on the parts where you feel you are weakest.
-    Read [Chapter 1 of the textbook](http://OTexts.com/fpp3/intro.html) and watch all embedded videos. Pay particular attention to [Section 1.7](https://otexts.com/fpp3/perspective.html).
-   Read [Section 2.1 of the textbook](https://otexts.com/fpp3/tsibbles.html#tsibbles) and watch the embedded video.


```{r}
#| output: asis
# show_slides(week)
show_slides_ann(week)
show_activity(week, show_solutions = FALSE)
```

## Seminar Code

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [week1-code.R](Week1-code.R){download="week1-code.R"}
:::



## Tutorial exercises

::: {.callout-note collpase="true"}

## Tutorial Learning Objectives

1. Work confidently with Quarto documents. 
   - Open, run, and knit the IA_template.qmd file to PDF without errors.

2. Import and manage time series data in R. 
   - Read CSV/Excel files, correctly set your working directory, and avoid file path errors.

3. Create and understand `tsibbles`. 
    - Convert data frames to tsibbles using as_tsibble() and understand the time index and key variables.

4. Begin planning IA1. 
    - Start thinking about your forecasting approach and discuss ideas with peers.
  
:::

**Tutorial tasks:**

1. Walk through [IA_template.qmd](../week1/IA_template.qmd.zip). Make sure you understand the quarto (qmd) file structure and make sure you can knit the file successfully to pdf format.
2. Discuss [IA1](https://bf.numbat.space/assignments/A1.html) in class. How do you go about forecasting at the moment that you are untrained? 
3. Complete Exercises 1, 3 and 5 from [Section 2.10 of the textbook](https://otexts.com/fpp3/graphics-exercises.html).

Your tutors will be in your tutorial class to assist you. 

-   <i class="bi bi-download"></i> [Week 1 Tutorial Solution.html](Week2.html){download="Tutorial1Solution.html"}


```{r}
#| output: asis
show_assignments(week)
```
