---
title: "Week 2: Time series graphics"
---

```{r}
#| cache: false
week <- 2
source(here::here("course_info.R"))
```


## What you will learn this week

* Different types of plots for time series including time plots, season plots, subseries plots, lag plots and ACF plots.
* The difference between seasonal patterns and cyclic patterns in time series.
* What is "white noise" and how to identify it.



## Pre-class activities

-   Read [Chapter 2 of the textbook](https://otexts.com/fpp3/graphics.html) and watch all embedded videos


```{r}
#| output: asis
#show_slides(week)
show_slides_ann(week)
show_activity(week, show_solutions = FALSE)
```

## Seminar Code

::: {.callout appearance="minimal"}
<!-- <i class="bi bi-download"></i> [week2-code-incomplete.R](week2-code-incomplete.R){download="week2-code-incomplete.R"} -->
<i class="bi bi-download"></i> [week2-code.R](week2-code.R){download="week2-code.R"}
:::



## Tutorial exercises

::: {.callout-note}

## Tutorial Learning Objectives

1. **Apply time series visualisation techniques**. 
    - Able to create and interpret a range of graphical displays (time plots, seasonal plots, lag plots, and ACF plots) to explore patterns in time series data.

2. **Identify and explain key time series features**. 
    - Analyse visual outputs to detect trend, seasonality, autocorrelation, structural changes, and outliers.

3. **Identify white noise behaviour**. 
    - Use differenced data and ACF plots to determine whether a time series exhibits characteristics of white noise.

:::

-   Complete Exercises 6, 7, 11 from [Section 2.10 of the book](https://otexts.com/fpp3/graphics-exercises.html).
-   <i class="bi bi-download"></i> [Week 2 Tutorial Solution.html](Tutorial2Solution.html){download="Tutorial2Solution.html"}


<!-- ```{r} -->
<!-- #| output: asis -->
<!-- show_slides(week) -->
<!-- ``` -->

<!-- ## Lectorial activities -->

<!-- ```{r} -->
<!-- #| child: activities.qmd -->
<!-- ``` -->


<!-- ## Seminar code -->

<!-- ::: {.callout appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [week2.R](week2.R){download="week2.R"} -->
<!-- ::: -->



```{r, echo=FALSE}
#| output: asis

show_assignments(week)
```
