---
title: "Week 4: The forecaster's toolbox"
---

```{r}
week <- 4
source(here::here("course_info.R"))
```

## What you will learn this week

* Forecasting workflow
* Four benchmark forecasting methods that we will use for comparison
* Linear trends, dummy seasonality
* Fitted values, residuals
* Forecasting using transformations
* Forecasting with decompositions
* Forecast evaluation

## Pre-seminar activities

* Read [Chapter 5 of the textbook](https://otexts.com/fpp3/toolbox.html) and watch all embedded videos
* Read [Chapter 7.4 of the textbook](https://otexts.com/fpp3/useful-predictors.html) and watch the embedded video. Ignore Fourier series for the moment. 

## Tutorial exercises (in class or on your own)

* Complete Exercises 1, 3, 5, 11  from [Section 5.11 of the book](https://otexts.com/fpp3/toolbox-exercises.html).
* Complete Exercise 2 from [Section 7.10 of the book](https://otexts.com/fpp3/regression-exercises.html).
* [Tutorial learning objectives](tute-lo.qmd).

<!-- -   <i class="bi bi-download"></i> [Week 4 Tutorial Solution.html](Week4.html){download="Week 4 Tutorial Solution.html"} -->


<!-- # ```{r} -->
<!-- # #| output: asis -->
<!-- # show_slides(week) -->
<!-- # ``` -->

<!-- ## Lectorial activities -->

<!-- ```{r} -->
<!-- #| child: activities.md -->
<!-- ``` -->


<!-- ## Seminar code -->

<!-- ::: {.callout appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [week4.R](week4.R){download="week4.R"} -->
<!-- ::: -->



```{r, echo=FALSE}
#| output: asis

show_assignments(week)
```
