---
title: "Week 4: The forecaster's toolbox"
---

```{r}
week <- 4
source(here::here("course_info.R"))
```

## Tutorial exercises

-   Complete Exercise 2, 3, 10 from [Section 3.7](https://otexts.com/fpp3/decomposition-exercises.html) of the book.
-   [Tutorial learning objectives](tute-lo.qmd).
<!-- -   <i class="bi bi-download"></i> [Week 4 Tutorial Solution.html](Week4.html){download="Week 4 Tutorial Solution.html"} -->

## What you will learn this week

* Forecasting workflow
* Four benchmark forecasting methods that we will use for comparison
* Linear trends, dummy seasonality
* Fitted values, residuals
* Forecasting using transformations
* Forecasting with decompositions
* Evaluating forecasts


## Pre-seminar activities

* Read [Chapter 5 of the textbook](https://otexts.com/fpp3/toolbox.html) and watch all embedded videos
* Read [Chapter 7.4 of the textbook](https://otexts.com/fpp3/useful-predictors.html) and watch the embedded video. Ignore Fourier series for the moment. 

# ```{r}
# #| output: asis
# show_slides(week)
# ```

## Lectorial activities

```{r}
#| child: activities.md
```


## Seminar code

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [week4.R](week4.R){download="week4.R"}
:::



```{r, echo=FALSE}
#| output: asis

show_assignments(week)
```
