---
title: "Week 3: Time series decomposition"
---

```{r}
week <- 3
source(here::here("course_info.R"))
```

## What you will learn this week

* Transforming data to remove some sources of variation
* Decomposing a time series into trend-cycle, seasonal and remainder components
* Seasonal adjustment

## Pre-seminar activities

Read [Chapter 3 of the textbook](https://otexts.com/fpp3/decomposition.html) and watch all embedded videos


## Tutorial exercises (in class or on your own)

::: {.callout-note collpase="true"}

1. **Visualise and assess time series transformations**. 
    - Create appropriate graphs for multiple time series and apply transformations when needed.
    
2. **Evaluate the usefulness Box–Cox transformations**. 
    - Able to explain when and why a Box–Cox transformation is or is not helpful for a given dataset.
    
3. **Apply time series decomposition techniques**. 
    - Able to decompose a time series into trend, seasonal, and remainder components using STL decomposition and interpret the results.
    

:::

-   Complete Exercise 2, 3, 10 from [Section 3.7](https://otexts.com/fpp3/decomposition-exercises.html) of the book.
-   [Tutorial learning objectives](tute-lo.qmd).
<!-- -   <i class="bi bi-download"></i> [Week 3 Tutorial Solution.html](Week3.html){download="Week 3 Tutorial Solution.html"} -->



<!-- ```{r} -->
<!-- #| output: asis -->
<!-- show_slides(week) -->
<!-- ``` -->

<!-- ## Lectorial activities -->

<!-- ```{r} -->
<!-- #| child: activities.md -->
<!-- ``` -->


<!-- ## Seminar code -->

<!-- ::: {.callout appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [week3.R](week3.R){download="week3.R"} -->
<!-- ::: -->



```{r, echo=FALSE}
#| output: asis

show_assignments(week)
```
