---
title: "Week 5: Exponential smoothing"
---

```{r}
week <- 5
source(here::here("course_info.R"))
```

## Tutorial exercises

-   Complete Exercises 1, 3, 5, 11  from [Section 5.11 of the book](https://otexts.com/fpp3/toolbox-exercises.html).
-   [Tutorial learning objectives](tute-lo.qmd).
<!-- -   <i class="bi bi-download"></i> [Week 5 Tutorial Solution.html](Week5.html){download="Week 5 Tutorial Solution.html"} -->

## What you will learn this week

* Simple exponential smoothing and corresponding ETS models.
* Methods with trend and corresponding ETS models.


## Pre-class activities

Read [Sections 8.1-8.4 of the textbook](https://otexts.com/fpp3/expsmooth.html) and watch all embedded videos

# ```{r}
# #| output: asis
# show_slides(week)
# ```

## Seminar activities

```{r}
#| child: activities.md
```


## Seminar code

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [week5.R](week5.R){download="week5.R"}
:::



```{r, echo=FALSE}
#| output: asis

show_assignments(week)
```
